---
title: "Two dimensional visualization of kultarr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{twod_vis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(kultarr)
library(randomForest)
library(dplyr)
library(tidyr)
library(kumquat)
library(ggplot2)

set.seed(145)
data("d_multitwo")
train_data <- d_multitwo
rf_model <- randomForest(class ~ ., data = train_data)

model_func <- carrier::crate(function(data) {
  return(randomForest:::predict.randomForest(!!rf_model, data))
})

find_closest <- function(pt, data) {
  dst <- data |>
    mutate(dst = sqrt((x - pt$x)^2 + (y - pt$y)^2))
  return(which.min(dst$dst))
}
obs <- find_closest(tibble(x = 0, y = 0), train_data)

final_bounds <- make_anchors(
  dataset = train_data,
  cols = c("x", "y"),
  instance = train_data[obs, ],
  model_func = model_func,
  class_col = "class",
  verbose = FALSE
)
```

The returned object has several parts in it. For visualisation we would primarily need the final_anchor and the perturbations used in it.

kultarr has a convenience function called `rule_rect_layers`, which when given a tibble containing the bounds of either the anchors or the perturbations, will create a `geom_rect` object that can be used in ggplot visualisations.

<!-- TODO: The model predictions should be used as the background. Check this in the README, and the tourd. -->

This one is on the lower end 

```{r}
model_fit <- expand_grid(x = seq(-1, 1, length.out = 50), y = seq(-1, 1, length.out = 50))
model_fit$pred <- model_func(model_fit)

ggplot() +
  geom_point(data = model_fit, mapping = aes(x = x, y = y, colour = pred), alpha = 0.1) +
  rule_rect_layers(final_bounds$perturb_bounds, fill = "gray", alpha = 0.5) +
  rule_rect_layers(final_bounds$final_anchor, fill = "black", alpha = 0.8) +
  geom_point(data = train_data[obs, ], mapping = aes(x = x, y = y, colour = class), size = 2, shape = 19, fill = "black") +
  theme_minimal() +
  coord_equal()
```

```{r}
obs <- find_closest(tibble(x = 0, y = 0.1), train_data)

final_bounds <- make_anchors(
  dataset = train_data,
  cols = c("x", "y"),
  instance = train_data[obs, ],
  model_func = model_func,
  class_col = "class",
  verbose = FALSE
)
```

This one is right on the boundary

```{r}
ggplot() +
  geom_point(data = model_fit, mapping = aes(x = x, y = y, colour = pred), alpha = 0.1) +
  rule_rect_layers(final_bounds$perturb_bounds, fill = "gray", alpha = 0.5) +
  rule_rect_layers(final_bounds$final_anchor, fill = "black", alpha = 0.8) +
  geom_point(data = train_data[obs, ], mapping = aes(x = x, y = y, colour = class), size = 2, shape = 19, fill = "black") +
  theme_minimal() +
  coord_equal()
```


```{r}
obs <- find_closest(tibble(x = 0, y = 0.2), train_data)

final_bounds <- make_anchors(
  dataset = train_data,
  cols = c("x", "y"),
  instance = train_data[obs, ],
  model_func = model_func,
  class_col = "class",
  verbose = FALSE
)
```
```{r}
ggplot() +
  geom_point(data = model_fit, mapping = aes(x = x, y = y, colour = pred), alpha = 0.1) +
  rule_rect_layers(final_bounds$perturb_bounds, fill = "gray", alpha = 0.5) +
  rule_rect_layers(final_bounds$final_anchor, fill = "black", alpha = 0.7) +
  geom_point(data = train_data[obs, ], mapping = aes(x = x, y = y, colour = class), size = 2, shape = 19, fill = "black") +
  theme_minimal() +
  coord_equal()
```

Try six more different places, some from the axis parallel places etc.

```{r}
ggplot() +
  geom_point(data = final_bounds$perturbs, mapping = aes(x = x, y = y, color = preds)) +
  rule_rect_layers(final_bounds$final_anchor) +
  geom_point(data = train_data[21, ], mapping = aes(x = x, y = y), size = 2, shape = 19, fill = "black") +
  theme_minimal()
```
